% !TeX root = ../technical_paper.tex
% ================= 参考文献 =================
\addcontentsline{toc}{section}{参考文献}
\section*{参考文献}

\begin{enumerate}[label={[\arabic*]}, leftmargin=*, itemsep=0.6ex]
  \item Erickson R W, Maksimovic D. Fundamentals of Power Electronics. 2nd ed. New York: Springer, 2001.
  \item Rashid M H. Power Electronics: Circuits, Devices, and Applications. 4th ed. Pearson, 2014.
  \item Liu Fangrui, Duan Shanxu, Liu Fei, Liu Bangyin, Kang Yong. A variable step size INC MPPT method for PV systems. IEEE Transactions on Industrial Electronics, 2008, 55(7): 2622--2628.
  \item Hohm D P, Ropp M E. Comparative study of maximum power point tracking algorithms. Progress in Photovoltaics: Research and Applications, 2003, 11(1): 47--62.
  \item Meshkati E, Packnezhad M, Farzanehfard H, Khajehoddin S A. Soft switched high step-up multi-port converter with single magnetic core and auxiliary switch for renewable energy applications. IEEE Transactions on Industrial Electronics, 2025, 72(1): 288--298.
  \item Cao J, Emadi A. A new battery/ultracapacitor hybrid energy storage system for electric, hybrid, and plug-in hybrid electric vehicles. IEEE Transactions on Power Electronics, 2012, 27(1): 122--132.
  \item Plett G L. Battery Management Systems, Volume I: Battery Modeling. Boston: Artech House, 2015.
  \item Plett G L. Battery Management Systems, Volume II: Equivalent-Circuit Methods. Boston: Artech House, 2015.
  \item Teodorescu R, Liserre M, Rodriguez P. Grid Converters for Photovoltaic and Wind Power Systems. Chichester: Wiley, 2011.
  \item Esram T, Chapman P L. Comparison of photovoltaic array maximum power point tracking techniques. IEEE Transactions on Energy Conversion, 2007, 22(2): 439--449.
  \item Femia N, Petrone G, Spagnuolo G, Vitelli M. Optimization of perturb and observe maximum power point tracking method. IEEE Transactions on Power Electronics, 2005, 20(4): 963--973.
  \item Azuatalam D, Paridari K, Ma Y, Forstl M, Chapman A C, Verbic G. Energy management of small-scale PV-battery systems: A systematic review considering practical implementation, computational requirements, quality of input data and battery degradation. Applied Energy, 2019, 254: 113677.
  \item Xing Y, Ma E W M, Tsui K L, Pecht M. Battery management systems in electric and hybrid vehicles. Energies, 2011, 4(11): 1840--1857.
  \item Yilmaz M, Krein P T. Review of battery charger topologies, charging power levels, and infrastructure for plug-in electric and hybrid vehicles. IEEE Transactions on Power Electronics, 2013, 28(5): 2151--2169.
  \item Gungor V C, Sahin D, Kocak T, Ergut S, Buccella C, Cecati C, Hancke G P. Smart grid technologies: Communication technologies and standards. IEEE Transactions on Industrial Informatics, 2011, 7(4): 529--539.
  \item Hu X, Li S, Peng H. A comparative study of equivalent circuit models for Li-ion batteries. Journal of Power Sources, 2012, 198: 359--367.
  \item Zhang Y, Liu W, Zhu C. State of charge estimation for lithium-ion batteries using neural network and EKF. IEEE Transactions on Power Electronics, 2020, 35(10): 10536--10547.
  \item Shen W, Vo T T, Kapoor A. Charging algorithms of lithium-ion batteries: An overview. IEEE Industrial Electronics Conference (IECON), 2012: 1567--1572.
  \item Baronti F, Roncella R, Saletti R. Performance analysis of active balancing hardware for lithium-ion battery cells. IEEE Transactions on Power Electronics, 2014, 29(8): 3948--3956.
  \item Lu L, Han X, Li J, Hua J, Ouyang M. A review on the key issues for lithium-ion battery management in electric vehicles. Journal of Power Sources, 2013, 226: 272--288.
  \item Chen X, Shen W, Vo T T, Kapoor A. State of charge estimation of lithium-ion batteries based on improved H infinity observer. International Journal of Electrical Power \& Energy Systems, 2021, 129: 106788.
  \item Xiong R, Sun F, Chen Z, He H. A data-driven multi-scale extended Kalman filtering based parameter and state estimation approach of lithium-ion polymer battery in electric vehicles. Applied Energy, 2014, 113: 463--476.
  \item Zhao Y, Liu W, Gao Y, Lyu W. State of charge estimation based on coulomb counting with an improved open-circuit voltage approach. Energies, 2022, 15(3): 1024.
\end{enumerate}

